### 2013-06-07 Tex/chapters/model.tex
mehr Text und Anmerkungen

\subsection{Critical Temperature $T_c$ and Critical Exponents}
    Because the searched for property -- the critical temperature \(T_c\)
    -- is only defined for infinite systems, hence every computer
    simulation will show some \emph{finte size effects}.
    [vielleicht Bild von intensiver Größe?]
    Despite of this one can obtain \(T_c\) by finite size scaling
    methods \cite[S. ??]{Newman1998} which also yield the critical
    exponents. The critical exponents should not be influenced by the
    disturbance paramter \(\sigma\) [citation needed]. So they will be
    used for consistency cross checking and comparision with the known
    exact values.\\
    [weiter ausarbeiten] [sagen, dass man für zwei/drei sigma
    die exponenten reproduziert hat].\\
    Though if one is just interested in the critical Temperature an
    easier approach is to find the intersections of the binder cumulants
    \(g = (3-\frac{<m^4>}{2<m^2>^2}\) \cite{Binder1981} of different
    system sizes \(L=\sqrt N\).\\

>>>>

\subsection{Critical Temperature $T_c$ and Critical Exponents}
    Because the searched for property -- the critical temperature \(T_c\)
    -- is only defined for infinite systems, hence every computer
    simulation will show some \emph{finte size effects}.
    [vielleicht Bild von intensiver Größe?]
    Despite of this one can obtain \(T_c\) by finite size scaling
    methods \cite[S. ??]{Newman1998} which also yield the critical
    exponents. The critical exponents should not be influenced by the
    disturbance paramter \(\sigma\) [citation needed]. So they will be
    used for consistency cross checking and comparision with the known
    exact values.\\
    [theorie mit dem Collaps]
    [Erklärung autoscale]
    [Am besten hier direkt die ganze Auswertung rein]
    [weiter ausarbeiten] [sagen, dass man für zwei/drei sigma
    die exponenten reproduziert hat].\\
    Though if one is just interested in the critical Temperature an
    easier approach is to find the intersections of the binder cumulants
    \(g = (3-\frac{<m^4>}{2<m^2>^2}\) \cite{Binder1981} of different
    system sizes \(L=\sqrt N\).
    Therefore a polynom of degree 4 is fitted to \(g\) in vicinity of
    the intersection. [vgl. Grafik (villeicht)]
    %The arithmetic average of the intersections are plotted [hier schon?]
    [Und den rest der Auswertung]
    \\
